OSMAC_Method; Model: `r params$Model_Path`; 

### 2023-02-26 Non_Identical_r0/Rmarkdown/OSMAC_Method.Rmd
Model information recalculated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning=FALSE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(gganimate)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(data.table)
library(ggpubr)

@@

FullDataPath<-here("Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = binomial)
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

@@

## Real Model Data

```{r Load Data}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output.RData"))

@@

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

## Assumed Model Data

### Old Probabilities

```{r Load Data Assumed Models}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_Old_1.RData"))

Est_Parameter_AM_Old_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_1)<-colnames(Est_Bias_AM_Old_1)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 2
load(here(Path,"OSMAC_output_Old_2.RData"))

Est_Parameter_AM_Old_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_2)<-colnames(Est_Bias_AM_Old_2)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

@@

load(here(Path,"OSMAC_output_Old_3.RData"))

Est_Parameter_AM_Old_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_3)<-colnames(Est_Bias_AM_Old_3)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

### New Probabilities

```{r Load Data Assumed Models 2}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_New_1.RData"))

Est_Parameter_AM_New_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_1)<-colnames(Est_Bias_AM_New_1)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 2
load(here(Path,"OSMAC_output_New_2.RData"))

Est_Parameter_AM_New_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_2)<-colnames(Est_Bias_AM_New_2)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 3
load(here(Path,"OSMAC_output_New_3.RData"))

Est_Parameter_AM_New_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_3)<-colnames(Est_Bias_AM_New_3)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

## Model Free

```{r Load Data Model Free}
Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","ModelFree/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_MF<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_MF<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_MF<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_MF)<-colnames(Est_Bias_MF)<-c("Type","Subsample_Size",
                                                             paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_MF)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

```{r Combine all datasets}
Est_Parameter<-rbind(cbind(Model="Real",Est_Parameter_RM),
                     cbind(Model="Assumed Old 1",Est_Parameter_AM_Old_1),
                     cbind(Model="Assumed Old 2",Est_Parameter_AM_Old_2),
                     cbind(Model="Assumed Old 3",Est_Parameter_AM_Old_3),
                     cbind(Model="Assumed New 1",Est_Parameter_AM_New_1),
                     cbind(Model="Assumed New 2",Est_Parameter_AM_New_2),
                     cbind(Model="Assumed New 3",Est_Parameter_AM_New_3),
                     cbind(Model="Model Free",Est_Parameter_MF))

remove(Est_Parameter_RM,Est_Parameter_MF,
       Est_Parameter_AM_Old_1,Est_Parameter_AM_Old_2,Est_Parameter_AM_Old_3,
       Est_Parameter_AM_New_1,Est_Parameter_AM_New_2,Est_Parameter_AM_New_3)

Est_Bias<-rbind(cbind(Model="Real",Est_Bias_RM),
                cbind(Model="Assumed Old 1",Est_Bias_AM_Old_1),
                cbind(Model="Assumed Old 2",Est_Bias_AM_Old_2),
                cbind(Model="Assumed Old 3",Est_Bias_AM_Old_3),
                cbind(Model="Assumed New 1",Est_Bias_AM_New_1),
                cbind(Model="Assumed New 2",Est_Bias_AM_New_2),
                cbind(Model="Assumed New 3",Est_Bias_AM_New_3),
                cbind(Model="Model Free",Est_Bias_MF))

remove(Est_Bias_RM,Est_Bias_MF,
       Est_Bias_AM_Old_1,Est_Bias_AM_Old_2,Est_Bias_AM_Old_3,
       Est_Bias_AM_New_1,Est_Bias_AM_New_2,Est_Bias_AM_New_3)

Utility<-rbind(cbind(Model="Real",Utility_RM),
               cbind(Model="Assumed Old 1",Utility_AM_Old_1),
               cbind(Model="Assumed Old 2",Utility_AM_Old_2),
               cbind(Model="Assumed Old 3",Utility_AM_Old_3),
               cbind(Model="Assumed New 1",Utility_AM_New_1),
               cbind(Model="Assumed New 2",Utility_AM_New_2),
               cbind(Model="Assumed New 3",Utility_AM_New_3),
               cbind(Model="Model Free",Utility_MF))

remove(Utility_RM,Utility_MF,
       Utility_AM_Old_1,Utility_AM_Old_2,Utility_AM_Old_3,
       Utility_AM_New_1,Utility_AM_New_2,Utility_AM_New_3)
```

@@

```{r Animated Plot for Parameter}
Est_Parameter %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Model), frame=Subsample_Size,fill=factor(Model))) + 
  geom_histogram(binwidth = 0.02,alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
```

@@

```{r Animated Plots for Bias RM}
Est_Bias %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Model), frame=Subsample_Size,fill=factor(Model))) + 
  geom_histogram(binwidth = 0.01,alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
```

@@

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Utility %>%
  ggplot(.,aes(x=log(A_optimality),fill=Model))+
  geom_histogram()+facet_grid(~factor(Type))+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))

Utility %>%
  ggplot(.,aes(x=log(D_optimality),fill=Model))+
  geom_histogram()+facet_grid(~factor(Type))+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
```

@@

# Summarise A- optimality
Utility %>%
  dplyr::select(Type,Model,Subsample_Size,A_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Utility %>%
  dplyr::select(Type,Model,Subsample_Size,D_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

@@

Accuracy<-apply(Parameter_Data,1,Predict_Logistic_Regression)
Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:3],Accuracy)
Accuracy_Data<-Accuracy_Data %>% 
  group_by(Model,Type,Subsample_Size) %>%
  summarize(Average_Accuracy=mean(Accuracy))

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

@@

```{r Final plots 1,fig.height=7,fig.width=20}
Plot_List<-list()

All_MSE %>%
  #ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_List[[1]]

All_MSE_MLE %>%
  #ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_List[[2]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_List[[3]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_List[[4]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_List[[5]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_List[[6]]

Accuracy_Data %>% 
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Accuracy")+ggtitle("Average Accuracy")->Plot_List[[7]]

ggarrange(plotlist = Plot_List,common.legend = TRUE,nrow=1)

```

@@

```{r Final plots 2,fig.height=7,fig.width=25}
Plot_List<-list()

All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_List[[1]]

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning=FALSE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(gganimate)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(data.table)

@@

FullDataPath<-here("Non_Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = binomial)
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

@@

# Real Model Data

```{r Load Data}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output.RData"))

@@

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

# Assumed Model 1

```{r Load the Data AM 1}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_1/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_1)<-colnames(Est_Bias_AM_1)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

# Assumed Model 2

```{r Load the Data AM 2}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_2/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_2)<-colnames(Est_Bias_AM_2)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

@@

```{r Load the Data AM 3}
Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_3/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_3)<-colnames(Est_Bias_AM_3)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

```{r Combine datasets}
# Combine datasets
Est_Parameter<-rbind(data.frame("Model"="Real Model",Est_Parameter_RM),
                     data.frame("Model"="Assumed Model 1",Est_Parameter_AM_1),
                     data.frame("Model"="Assumed Model 2",Est_Parameter_AM_2),
                     data.frame("Model"="Assumed Model 3",Est_Parameter_AM_3))

Est_Bias<-rbind(data.frame("Model"="Real Model",Est_Bias_RM),
                data.frame("Model"="Assumed Model 1",Est_Bias_AM_1),
                data.frame("Model"="Assumed Model 2",Est_Bias_AM_2),
                data.frame("Model"="Assumed Model 3",Est_Bias_AM_3))

Est_Utility<-rbind(data.frame("Model"="Real Model",Utility_RM),
                   data.frame("Model"="Assumed Model 1",Utility_AM_1),
                   data.frame("Model"="Assumed Model 2",Utility_AM_2),
                   data.frame("Model"="Assumed Model 3",Utility_AM_3))

remove(Est_Bias_AM_1,Est_Bias_AM_2,Est_Bias_AM_3,Est_Bias_RM,
       Est_Parameter_AM_1,Est_Parameter_AM_2,Est_Parameter_AM_3,Est_Parameter_RM,
       Utility_AM_1,Utility_AM_2,Utility_AM_3,Utility_RM)
```

@@

```{r Animated Plots}
Est_Parameter %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated,  frame=Subsample_Size,fill=as.factor(Model))) + 
  geom_histogram(binwidth = 0.02,alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
```

@@

```{r Animated Plots for Bias}
Est_Bias %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, frame=Subsample_Size,fill=Model)) + 
  geom_histogram(binwidth = 0.01,alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
```

@@

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Est_Utility %>%
  ggplot(.,aes(x=log(A_optimality),fill=Model))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))

Est_Utility %>%
  ggplot(.,aes(x=log(D_optimality),fill=Model))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
```

## Response Data of the Subsamples

```{r Response Data RM,eval=FALSE}
Random_Sample_RM[Random_Sample_RM$Subsample_Size==1500,] %>%
  select(Type,Simulation,Y) %>%
  group_by(Simulation,Type) %>%
  dplyr::count(Y)-> Response

remove_missing(Response) %>% 
  ggplot(.,aes(x=Simulation,y=n,fill=as.factor(Y)))+
  geom_bar(stat = "identity")+facet_wrap(~Type)+
  scale_fill_viridis_d()+theme_light()+
  ylab("Count / Frequency")+xlab("Simulation")+
  labs(fill=c("Response Variable"))+
  ggtitle("Real Model : Dispersion of Y variable after multiple simulations")
```

@@

# Summarise A- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,A_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,D_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

@@

Accuracy<-apply(Parameter_Data,1,Predict_Logistic_Regression)

Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:3],Accuracy)
Accuracy_Data<-Accuracy_Data %>% 
  group_by(Model,Type,Subsample_Size) %>%
  summarize(Average_Accuracy=mean(Accuracy))

@@

# Store the Results
save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

@@

```{r Final plots 1,fig.width=9,fig.height=24}
Plot_list<-list()

All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_list[[1]]

All_MSE_MLE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_list[[2]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[3]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[4]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[5]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[6]]

Accuracy_Data %>% 
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 2)+
  ylab("Average Accuracy")+ggtitle("Average Accuracy")->Plot_list[[7]]

ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
```

@@

```{r Final plots 2,fig.width=9,fig.height=24}
Plot_list<-list()

All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_list[[1]]

All_MSE_MLE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]
